---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

op_domain <- Sys.getenv('onepass_domain')
op_email <- Sys.getenv('onepass_email')
op_secretkey <- Sys.getenv('onepass_secretkey')
op_masterpassword <- Sys.getenv('onepass_password')
```

# onepass

<!-- badges: start -->
<!-- badges: end -->

The *onepass* package provides an interface to 1Password Command Line Interface (CLI). Using this, you can query the list of credentials in your vault, as well as download usernames and passwords for them.

## Installation

You will require the [1Password CLI](https://1password.com/downloads/command-line/) installed on your computer. 

You can install the released version of onepass from [CRAN](https://CRAN.R-project.org) with:

```{r, eval=FALSE}
install.packages("onepass")
```

And the development version from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("jonlinca/onepass")
```

## Set up

Once the 1Password CLI is installed, you should be set. You will need your domain (*.1password.com), the email account, your master password, as well as your secret key. 

If this is a new machine, you will need to setup 1Password CLI with R. This will require both the master password and secret key:

```{r, message=FALSE}
library('onepass')

ops <- setup_op(op_domain, op_email, op_masterpassword, op_secretkey) 
```

For new machines, you may also receive the following as well:

```{r, echo = FALSE}
message("To reduce notifications of new devices, insert the following line into the \nRenviron file (usethis::edit_r_environ() or edit .Renviron):
          OP_DEVICE = 1234567890abcdefghijklmnopqrstuvwxyz")
```

If you receive the above message, its highly recommended that you insert the unique `OP_DEVICE` into your .Renviron file - otherwise, you will receive constant messages about logins from a new device.

## Usage

Once you have set up 1Password and connected to the vault, you can connect to 1Password by unlocking the vault. You will also need to do this if your session token expires after 30 minutes. The email isn't required.

```{r}
ops <- unlock_op(op_domain, op_masterpassword)
```

This `ops` object will contain three elements, the most important being the token. You can use this token and pass it through to see what vaults you have access to:

```{r, eval=FALSE}
op_list_vaults(ops)
```

Within these vaults, you can see the list of passwords you have available:

```{r, eval=FALSE}
op_list_items(ops) # All vaults
op_list_items(ops, 'Private') # Just the contents in the private vault
```

And most importantly, you can retrieve the username and password for any singular item. You can either use the name, or more reliably, the UUID:

```{r}
op_get_item(ops, 'Westjet')
op_get_item(ops, 'c4mqmdxk4gyjgifj5s5tctk4ea')
```
